\documentclass[letterpaper,10pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontspec}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Enes Kaynakcı} \\ \vspace{2pt}
    \small AI / Software Engineer \\ \vspace{2pt}
    \small Ankara, Türkiye ~\textbar~ \href{mailto:tensorenes@gmail.com}{\underline{tensorenes@gmail.com}} ~\textbar~
    \href{https://www.linkedin.com/in/enes-kaynakci/}{\underline{linkedin.com/in/enes-kaynakci}} ~\textbar~
    \href{https://github.com/ekaynac}{\underline{github.com/ekaynac}}
\end{center}

\section{Summary}
\small{AI-leaning full-stack engineer building LLM and agent pipelines and computer-vision systems on production microservices and modern web and mobile stacks. Bilkent University Information Systems graduate (2026).}
\vspace{-4pt}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Mega Bilgisayar}{May 2026 -- Present}{AI / Software Engineer}{Ankara, Türkiye}
\resumeItemListStart
\resumeItem{Build on-prem LLM platforms and agent tooling, including a customized LibreChat deployment (BukaUI) and MCP-based portal agents for internal workflows.}
\resumeItem{Designed LLMDAP, a sovereign LLM-agent identity and memory-protection library binding agent memory and tool access to AD/LDAP or OIDC identities with Casbin authorization, envelope encryption, and a tamper-evident audit trail.}
\resumeItem{Developed computer-vision industrial-safety systems (PPE/vest detection) on Advantech edge hardware using YOLO.}
\resumeItemListEnd
\resumeSubheading{Mia Teknoloji}{Feb 2025 -- Jul 2025}{AI Intern, AI R\&D}{Ankara, Türkiye}
\resumeItemListStart
\resumeItem{Engineered end-to-end LLM agent pipelines using RAG, function calling, transformers, and embedding models.}
\resumeItem{Delivered a production SQL-generation pipeline with a 3-tier fallback mechanism using OpenWebUI and local LLMs.}
\resumeItem{Built a Turkish translation pipeline integrating Zemberek morphology for improved contextual accuracy.}
\resumeItemListEnd
\resumeSubheading{Mega Bilgisayar}{Jun 2024 -- Aug 2024}{AI Solutions Team}{Ankara, Türkiye}
\resumeItemListStart
\resumeItem{Developed and deployed an industrial safety system using YOLOv5 and OpenCV on NVIDIA Jetson with TensorRT optimization.}
\resumeItemListEnd
\resumeSubheading{Meturone (Fixed-wing UAV Team)}{Sep 2021 -- Sep 2023}{Computer Vision Team Member}{Ankara, Türkiye}
\resumeItemListStart
\resumeItem{Teknofest International UAV Competition finalist (2021 and 2022); deployed FP16-quantized YOLOv5 on Jetson Xavier for real-time aerial perception.}
\resumeItem{Curated and published an \textasciitilde{}11,500-image (8,815 train / 2,650 validation) UAV detection dataset for open-source use.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-8pt}

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{SIMS — Smart Inventory Management System} $|$ \emph{PHP, Laravel, Node.js, Fastify, Python, FastAPI}}{\href{https://github.com/sims-1/sims}{\underline{Code}}}
\resumeItemListStart
\resumeItem{10-microservice inventory platform with an MCP-powered AI assistant (graduation project).}
\resumeItem{10 microservices across 4 languages with per-service databases and a Redis event bus.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{LLMDAP — LLM Directory-bound Access Protection} $|$ \emph{TypeScript, Node.js, Casbin, LDAP/Active Directory, OIDC, AES-256-GCM}}{\href{https://github.com/ekaynac/LLMDAP}{\underline{Code}}}
\resumeItemListStart
\resumeItem{Sovereign LLM-agent identity and memory protection bound to AD/LDAP or OIDC.}
\resumeItem{On-prem by default: LDAP identity, embedded Casbin, local encrypted storage, hash-chained audit.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{Etch-A-Chat} $|$ \emph{React Native, Expo, Skia, Socket.io, MongoDB, Redis}}{\href{https://github.com/ekaynac/EtchaMessage}{\underline{Code}}}
\resumeItemListStart
\resumeItem{Privacy-focused real-time vector-drawing messenger.}
\resumeItem{Live collaborative vector canvas over Socket.io.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-8pt}

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-2pt]
\small{\item{\textbf{Languages:} Python, TypeScript, JavaScript, PHP, Java, C, Dart, Kotlin}}
\small{\item{\textbf{AI \& ML:} LLM Pipelines, RAG, Function Calling, Agents, MCP, Transformers, Embeddings, DSPy, TensorFlow, PyTorch, OpenCV, TensorRT, YOLOv5}}
\small{\item{\textbf{Web \& Mobile:} React, Next.js, React Native (Expo), Node.js, Express, Fastify, FastAPI, Laravel, Socket.io, Tailwind CSS, Vite}}
\small{\item{\textbf{Infrastructure \& Tools:} Docker, Kubernetes (EKS), Nginx, MySQL, MongoDB, Redis, RabbitMQ, GitHub Actions, Git, Supabase, Vercel, LDAP/OIDC, Casbin}}
\end{itemize}
\vspace{-10pt}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Bilkent University}{Aug 2022 -- Jun 2026}{B.Sc. in Information Systems and Technologies}{Ankara, Türkiye}
\resumeSubheading{FH Upper Austria, Hagenberg Campus}{Oct 2024 -- Feb 2025}{Erasmus Exchange Student}{Hagenberg, Austria}
\resumeSubheading{Middle East Technical University (METU)}{Sep 2018 -- Jun 2021}{B.Sc. in Electrical-Electronics Engineering (transferred)}{Ankara, Türkiye}
\resumeSubHeadingListEnd
\vspace{-8pt}

\section{Certifications \& Awards}
\small{Deep Learning Specialization (DeepLearning.AI), Stanford Machine Learning; 2nd Place — 18th METU Robotics Days (Autonomous UAV CV, 2022); Teknofest UAV Finalist (2021 \& 2022).}
\vspace{-4pt}

\section{Leadership \& Interests}
\small{Founder, Bilkent Game Development \& Animation Society; President, Bilkent Literature Society; founding poetry editor at Polemik Yayınları; published poet (Uyandı Uyudu, 2024).}
\vspace{-4pt}

\end{document}
